%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Edited Books and Journal Issues}


%-------------------------------------------------------------------------------
%	SUBSECTION TITLE
%-------------------------------------------------------------------------------
%\cvsubsection{International}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
%\begin{cvhonors}

%---------------------------------------------------------
%  \cvhonor
%    {Finalist} % Award
%    {DEFCON 26th CTF Hacking Competition World Final} % Event
%    {Las Vegas, U.S.A} % Location
%    {2018} % Date(s)
% \end{cvhonors}

\begin{cventries}
\begin{cvitems}
\item Antonucci, Alessandro and Corani, Giorgio and de Campos, Cassio Polpo (Eds) (2016), PGM 2016: Proceedings of the Eighth International Conference on Probabilistic Graphical Models. 6-9 September 2016, Lugano, Switzerland. Volume 52 of the JMLR Workshop and Conference Proceedings. PMLR.
\item Antonucci, Alessandro and Corani, Giorgio and Couso, Inés and Destercke, Sébastien (Eds) (2017), ISIPTA '17: Proceedings of the Tenth International Symposium on Imprecise Probability: Theories and Applications. 10-14 July 2017, Lugano, Switzerland. Volume 62 of the JMLR Workshop and Conference Proceedings. PMLR.
\item Antonucci, Alessandro and Cholvy, Laurence annd Papini, Odile (Eds) (20170. Symbolic and Quantitative Approaches to Reasoning with Uncertainty (Proceedings of the 14th European Conference on Symbolic and Quantitative Approaches to Reasoning with Uncertainty). Lugano, Switzerland, July 10–14, 2017, Lecture Notes in Artificial Intelligence, volume 10369. Springer.
\item Antonucci, Alessandro and Cholvy, Laurence annd Papini, Odile (Eds) International Journal of Approximate Reasoning {\bf{99}}. Special Issue on the 14th European Conference on Symbolic and Quantitative Approaches to Reasoning with Uncertainty (ECSQARU 2017).
\item Antonucci, Alessandro and Corani, Giorgio and Couso, Inés and Destercke, Sébastien (Eds) (2017), International Journal of Approximate Reasoning {\bf{105}}. Special Issue on Tenth International Symposium on Imprecise Probability: Theories and Applications (ISIPTA ’17).
\end{cvitems}
\end{cventries}
