%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {SLK Software Services Pvt. Ltd.} % Organization
    {Bangalore, India} % Location
    {Jul 2018 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {As a Software Engineer design and development of solutions for clients in a team environment. Technologies used are ASP.Net MVC,WebAPI,SSIS,Windows Service, MSSql Database.}
  \item {In SLK i am part of one Project Consolidated Claims View for the client Regions Bank. Consolidate Claims View will help bank associate and bank customer to raise the claims on miscellaneous transactions.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Capgemini
Technology Services India Limited} % Organization
    {Bangalore, India} % Location
    {Mar 2018 - Jul 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {As a Associate Consultant design and development of solutions for clients in a team environment. Technologies used are ASP.Net MVC,Entity Framework, Oracle Database.}
  \item {In Capgemini i was  part of one project Employee Portal Management for client American Electric Power(AEP).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Mindmaps Technologies Pvt.Ltd.} % Organization
    {Bangalore, India} % Location
    {Feb 2017 - Mar 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {As a Software Engineer responsible for Developing a Software as required by the customer need. Technologies used are ASP.Net WebApplication,MVC,WebApi, Entity Framework, Mysql Database.}
  \item {In Mindmaps i was part of three project where in needed to handle 4-5 team member in each project.}
  \item {Project are related to Bakery web site and Online Order management, Cracker Website and Online Order Management and Online portal for Registering for Higher Study.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer And Head Of Operation} % Job title
    {Rakya Technologies Pvt.Ltd.} % Organization
    {Bangalore, India} % Location
    {Jun 2015 - Jan 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {As a Software Engineer responsible for Developing, Updating and Maintaining the source code of Rakya Software. Technologies used are Dot Net Windows application, Mysql Database, WCF.}
  \item {As a Head of Operation manage the team to deliver the result for Customer facing issue.}
  \item {Products i owned to Develop and Update were Hospital Finance Management System, Patient lab report Management,Patient History Management and WCF communication channel maintenance for Patient notification.}
      \end{cvitems}
    }


%---------------------------------------------------------
\end{cventries}
