
\documentclass[11pt,a4paper]{moderncv}
\moderncvtheme[grey]{casual}              
% optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
%\moderncvtheme[green]{classic}                % idem
\usepackage{ucs}
\usepackage{url}
\usepackage[scale=0.8]{geometry}
\firstname{Alessandro}
\familyname{Antonucci}
\title{Publication list 2009 -- 2014}               % optional, remove the line if not wanted
\makeatletter
\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
\makeatother

\begin{document}

\maketitle
The full publication list is available at \url{www.idsia.ch/~alessandro}.

\section{Peer-reviewed articles on journals}
\begin{itemize}
\item Corani, G., Antonucci, A. (2014). \textit{Credal Ensembles of Classifiers}. Computational Statistics \& Data Analysis 71, pp. 818--831.
\item Antonucci, A., Yi, S., de Campos, C.P., Zaffalon, M. (2010). Generalized loopy 2U: a new algorithm for approximate inference in credal networks. International Journal of Approximate Reasoning 55(5), pp. 474--484.
\item Benavoli, A., Antonucci, A. (2010). Aggregating imprecise probabilistic knowledge: application to Zadeh's paradox and sensor networks. Int. Journal of Approximate Reasoning 51(9), pp. 1014--1028.
\item de Cooman, G., Hermans, F., Antonucci, A., Zaffalon, M. (2010). Epistemic irrelevance in credal nets: the case of imprecise markov trees. International Journal of Approximate Reasoning 51(9), pp. 1029--1052.
\item Antonucci, A., Br\"uhlmann, R., Piatti, A., Zaffalon, M. (2009). Credal networks for military identification problems. International Journal of Approximate Reasoning 50(2), pp. 666--679.
\end{itemize}

\section{Peer-reviewed articles in conference proceedings}
\begin{itemize}
\item Antonucci, A., de Campos, C.P., Huber, D., Zaffalon, M. (2013). Approximating credal network inferences by linear programming. In van der Gaag, L. C. (Ed), Proceedings of the 12th European Conference on Symbolic and Quantitative Approaches to Reasoning with Uncertainty, Lecture Notes in Artificial Intelligence 7958, Springer, Berlin Heidelberg, pp. 13--25.
\item Antonucci, A., Corani, G., Maua, D.D., Gabaglio, S. (2013). \textit{An ensemble of Bayesian networks for multilabel classification}. In Proceedings of the 23rd International Joint Conference on Artificial Intelligence (IJCAI-13), pp 1220--1225.
\item Antonucci, A., Huber, D., Zaffalon, M., Luginbuehl, P., Chapman, I., Ladouceur, R. (2013). CREDO: a military decision-support system based on credal networks. In Proceedings of the 16th Conference on Information Fusion (FUSION 2013), pp. 1--8.
\item Antonucci, A., de Rosa, R., Giusti, A., Cuzzolin, F. (2013). Temporal data classification by imprecise dynamical models. In Cozman, F., Denoeux, T., Destercke, S., Seidenfeld, T. (Eds), ISIPTA '13: Proceedings of the Eighth International Symposium on Imprecise Probability: Theories and Applications, SIPTA, pp. 13--22.
\item Mau\'a, D.D., de Campos, C.P., Benavoli, A., Antonucci, A. (2013). On the complexity of strong and epistemic credal networks. In Proceedings of the 29th Conference on Uncertainty in Artificial Intelligence, AUAI Press, pp. 391--400.
\item Antonucci, A. (2012). An interval-valued dissimilarity measure for belief functions based on credal semantics. In Denoeux, T., Masson, M.-H. (Eds), Belief Functions: Theory and Applications, Advances in Intelligent and Soft Computing 164, Springer Berlin / Heidelberg, pp. 37--44.
\item Antonucci, A., Cattaneo, M.E.V.G., Corani, G. (2012). \textit{Likelihood-based robust classification with Bayesian networks.} In Communications in Computer and Information Science, Advances in Computational Intelligence 299(5), Springer, pp. 491--500.
\item Antonucci, A., Corani, G., Gabaglio, S. (2012). \textit{Active learning by the naive credal classifier.} In Cano, A., Gomez-Olmedo, M., Nielsen, T. (Eds), Proc. of the 6th European Workshop on Probabilistic Graphical Models (PGM 2012), pp. 3--10.
\item Corani, G., Antonucci, A., De Rosa, R. (2012). \textit{Compression-based AODE classifiers}. In De Raedt, L. et al. (Ed), Proc. 20th European Conference on Artificial Intelligence (ECAI 2012), pp. 264--269.
\item Antonucci, A. (2011). The imprecise noisy-or gate. In FUSION 2011: Proceedings of the 14th International Conference on Information Fusion, IEEE, pp. 709--715.
\item Antonucci, A., de Campos, C.P. (2011). Decision making by credal nets. In Proceedings of the International Conference on Intelligent Human-machine Systems and Cybernetics (IHMSC 2011) 1, IEEE, Hangzhou (China), pp. 201--204.
\item Antonucci, A., Cattaneo, M., Corani, G. (2011). \textit{Likelihood-based naive credal classifier.} In ISIPTA '11: Proceedings of the Seventh International Symposium on Imprecise Probability: Theories and Applications, SIPTA, pp. 21--30.
\item Antonucci, A., de Rosa, R., Giusti, A. (2011). Action recognition by imprecise hidden markov models. In Proceedings of the 2011 International Conference on Image Processing, Computer Vision and Pattern Recognition, IPCV 2011, CSREA Press, pp. 474--478.
\item Antonucci, A., Cuzzolin, F. (2010). Credal sets approximation by lower probabilities: application to credal networks. In Hüllermeier, E., Kruse, R., Hoffmann, F. (Eds), Computational Intelligence for Knowledge-based Systems Design, 13th International Conference on Information Processing and Management of Uncertainty, IPMU 2010, Dortmund, Germany, June 28 - July 2, 2010. Proceedings, Lecture Notes in Computer Science 6178, Springer, pp. 716--725.
\item Antonucci, A., Benavoli, A., Zaffalon, M., de Cooman, G., Hermans, F. (2009). Multiple model tracking by imprecise markov trees. In FUSION 2009: Proceedings of the 12th International Conference on Information Fusion, IEEE.
\item Antonucci, A., Piatti, A. (2009). Modeling unreliable observations in Bayesian networks by credal networks. In Godo, L., Pugliese, A. (Eds), Scalable Uncertainty Management, Third International Conference, SUM 2009, Washington, DC, USA. Proceedings, Lecture Notes in Computer Science 5785, Springer, pp. 28--39.
\item Benavoli, A., Antonucci, A. (2009). Aggregating imprecise probabilistic knowledge. In ISIPTA '09: Proceedings of the Sixth International Symposium on Imprecise Probability: Theories and Applications, Durham (UK), pp. 31--41.
\end{itemize}
\section{Book contributions} 
\begin{itemize}
\item Antonucci, A., de Campos, C.P., Zaffalon, M. (2014). Probabilistic graphical models. In Augustin,T., Coolen,F., de Cooman,G., Troffaes,M. (Eds), Introduction to Imprecise Probabilities, Wiley, pp. 207--229.
\item Corani, G., Antonucci, A., Zaffalon, M. (2012). \textit{Bayesian networks with imprecise probabilities: theory and application to classification}. In Holmes, D.E., Jain, L.C. (Eds), Data Mining: Foundations and Intelligent Paradigms, Intelligent Systems Reference Library 23, Springer, Berlin / Heidelberg, pp. 49--93.
\item Piatti, A., Antonucci, A., Zaffalon, M. (2010). Building knowledge-based expert systems by credal networks: a tutorial. In Baswell, A.R. (Ed), Advances in Mathematics Research 11, Nova Science Publishers, New York.
\end{itemize}
\end{document}
