
%\begin{cventries}
%\cventry{Causal Expectation-Maximisation.}{Zaffalon, Marco and Antonucci, Alessandro and Cabañas, Rafael (2021).}
%{In WHY-21 Workshop (@ NeurIPS 2021). Virtual Event , Dec 13, 2021.}
%\end{cventries}

\cvsection{Publications}
\begin{cventries}
%  \cventry
%    {Bachelor of Engineering in  Electronics and Communication Engineering} % Degree
%    {Visvesvaraya Technological University } % Institution
%    {Belagavi , Karnataka} % Location
%    {Jun 2015} % Date(s)
%%    {
%      \begin{cvitems} % Description(s) bullet points
%       { }
%      \end{cvitems}
%    }

\begin{cvitems}
\item Causal Expectation-Maximisation. Zaffalon, Marco and Antonucci, Alessandro and Cabañas, Rafael (2021).
In WHY-21 Workshop (@ NeurIPS 2021). Virtual Event , Dec 13, 2021. 
 
\item Structural Learning of Probabilistic Sentential Decision Diagrams under Partial Closed-World Assumption. Antonucci, Alessandro and Facchini, Alessandro and Mattei, Lilith (2021). In The Fourth Tractable Probabilistic Modelling Workshop (@ UAI 2021). Virtual Event , Jul 30, 2021. 

\item ADAPQUEST: A Software for Web-Based Adaptive Questionnaires based on Bayesian Networks. Bonesana, Claudio and Mangili, Francesca and Antonucci, Alessandro (2021).
In AI4EDU: Artificial Intelligence For Education (@ IJCAI2021). Virtual Event , Aug 20, 2021. 

\item CREPO: An Open Repository to Benchmark Credal Network Algorithms Cabañas, Rafael and Antonucci, Alessandro (2021). In De Bock, J. and Cano, A. and Miranda, E. and Moral, S. (Eds),  International Symposium on Imprecise Probabilities: Theories and Applications (ISIPTA-2021). Grenada (Spain) , Jul 6-9, 2021.   147 ,  JMLR.org , 352–356 . 

\item A New score for Adaptive Tests in Bayesian and Credal Networks. Antonucci, Alessandro and Mangili, Francesca and Bonesana, Claudio and Adorni, Giorgia (2021). In Vejnarová, J. and Wilson, N. (Eds),  Symbolic and Quantitative Approaches to Reasoning With Uncertainty. Cham .  Springer International Publishing , 399–412 . 

\item Relation Clustering in Narrative Knowledge Graphs. Mellace, Simone and Kanjirangat, Vani and Antonucci, Alessandro (2021). In AI4Narratives Workshop at 29th International Joint Conference on Artificial Intelligence and the 17th Pacific Rim International Conference on Artificial Intelligence (IJCAI-PRICAI 20). . 

\item Robust Model Checking with Imprecise Markov Reward Models
Termine, Alberto and Antonucci, Alessandro and Facchini, Alessandro and Primiero, Giuseppe (2021).
In Proceedings of the Twelfth International Symposium on Imprecise Probabilities: Theories and Applications (ISIPTA ’21). Granada , Jul 6-9, 2021.  Proceedings of Machine Learning Research  147 ,  PMLR , 299–309 . 

\item Logic and Model Checking by imprecise Probabilistic Interpreted Systems
Termine, Alberto and Antonucci, Alessandro and Primiero, Giuseppe and Facchini, Alessandro (2021).
In Rosenfeld, A. and Talmon, N. (Eds),  Multi-Agent Systems. EUMAS 2021. Lecture Notes in Computer Science. Cham . 

\item Cautious Classification with Data Missing not at Random using Generative Random Forests
Llerena, Julissa V. and Mauá, Denis. D. and Antonucci, Alessandro (2021).
In Vejnarová, J. and Wilson, N. (Eds),  Symbolic and Quantitative Approaches to Reasoning With Uncertainty. Cham .  Springer International Publishing , 284–298 . 

\item Antonucci, Alessandro, and Tiotto, Thomas. Approximate MMAP by marginal search. In FLAIRS-33: Proceedings of the 33rd International Florida Artificial Intelligence Research Society Conference (2020), K. W. Brawner, R. Bart ́ak, and E. Bell, Eds., AAAI Press.
\item Mangili, Francesca, Broggini, Denis, Antonucci, Alessandro, Alberti, Marco, and Cimasoni, Lorenzo. A Bayesian approach to conversational recommendation systems. In AAAI 2020 Workshop on Interactive and Conversational Recommendation Systems (WICRS) (2020).
\item Vani K, Simone Mellace, Alessandro Antonucci (2020). Temporal embeddings and transformer models for narrative text understanding. Third International Workshop on Narrative Extraction from Texts (Text2Story 2020), 42nd European Conference on Information Retrieval.
\item Volpetti, Claudia and K, Vani and Antonucci, Alessandro (2020). \emph{Temporal word embeddings for narrative understanding}. In ICMLC 2020: Proceedings of the Twelfth International Conference on Machine Learning and Computing.   Shenzhen, China,   Feb 15-17 2020.   ACM.
\item Mattei, Lilith, Soares, Decio L., Antonucci, Alessandro, Mauà, Deratani Denis, Facchini, Alessandro (2019). Exploring the space of probabilistic sentential decision diagrams. In Proceedings of the 3rd Tractable Probabilistic Modeling Workshop, 36th International Conference on Machine Learning.
\item Antonucci, A., Facchini, A., Mattei, L. (2019). Credal sentential decision diagrams. In Proceedings of the Eleventh International Symposium on Imprecise Probability: Theories and Applications (ISIPTA '19).
\item Antonucci, Alessandro (2019).   Reliable discretisation of deterministic equations in Bayesian networks.   In Barták, Roman and Brawner, Keith W. (Eds), FLAIRS-32: Proceedings of the Thirty-Second International Florida Artificial Intelligence Research Society Conference.   Sarasota, Florida, USA,   May 19-22 2019.   AAAI Press.
\item Antonucci, Alessandro (2018).   Modeling Deterministic Equations in Discrete Bayesian Networks by Credal Networks.   J. Phys.: Conf. Ser. 1065.
\item Marchetti, Sabina and Antonucci, Alessandro (2018).   Reliable uncertain evidence modeling in Bayesian networks by credal networks.   In Brawner, Keith W. and Rus, Vasile (Eds), FLAIRS-31: Proceedings of the Thirty-First International Florida Artificial Intelligence Research Society Conference.   Melbourne, Florida, USA,   May 21-23 2018.   AAAI Press.
\item Marchetti, Sabina and Antonucci, Alessandro (2018).   Imaginary kinematics.   In Globerson, Amir and Silva, Ricardo (Eds), UAI 2018: Proceedings of the Thirty-Fourth Conference on Uncertainty in Artificial Intelligence.   Monterey, California, USA,   Aug 6-10 2018.   AUAI Press.
\item Antonucci, Alessandro and Facchini, Alessandro and Mattei, Lilith (2019).   Credal sentential decision diagrams.   In De Bock, Jasper and de Campos, Cassio Polpo and de Cooman, Gert and Quaeghebeur, Erik and Wheeler, Gregory (Eds), ISIPTA ’19: Proceedings of the Eleventh International Symposium on Imprecise Probabilities: Theories and Applications.   Ghent, Belgium, Jul 3-6 2019.   Proceedings of Machine Learning Research 103, PMLR, 14–22.
\item Antonucci, Alessandro and Facchini, Alessandro (2018).   A credal extension of independent choice logic.   In Ciucci, Davide and Pasi, Gabriella and Vantaggi, Barbara (Eds), Scalable Uncertainty Management (SUM 2018: Proceedings of the Twelfth International Conference on Scalable Uncertainty Management).   Milan, Italy, Oct 3-5 2018.   Lecture Notes in Artificial Intelligence 11142, Springer, Cham, 35–49.
\item Antonucci, Alessandro and Facchini, Alessandro (2018).   Set-valued probabilistic sentential decision diagrams.   In Bellodi, Elena and Schrijvers, Tom (Eds), Proceedings of the 5th Workshop on Probabilistic Logic Programming co-located with the 28th International Conference on Inductive Logic Programming (ILP 2018).   Ferrara, Italy,   Sep 1 2018.   CEUR Workshop Proceedings.
\item Mattei, Lilith and Soares, Décio L. and Antonucci, Alessandro and Mauà, Denis Deratani and Facchini, Alessandro (2019).   Exploring the space of probabilistic sentential decision diagrams.   In Proceedings of the third Tractable Probabilistic Modeling Workshop, 36th International Conference on Machine Learning, June 2019.   Long Beach, California, USA,   Jun 14 2019.
\item K, Vani and Antonucci, Alessandro (2019).   NOVEL2GRAPH: Visual summaries of narrative text enhanced by machine learning.   In Alípio, Mário Jorge and Ricardo, Campos and Adam, Jatowt and Sumit, Bhatia (Eds), Proceedings of Text2Story - Second Workshop on Narrative Extraction From Texts co-located with 41th European Conference on Information Retrieval (ECIR 2019).   Cologne, Germany,   Apr 14 2019.   CEUR Workshop Proceedings.
\item Mangili, Francesca and Bonesana, Claudio and Antonucci, Alessandro and Zaffalon, Marco and Rubegni, Elisa and Addimando, Loredana (2016).   Adaptive testing by Bayesian networks with application to language assessment.   In Micarelli, Alessandro and Stamper, John and Panourgia, Kitty (Eds), ITS 2016: Intelligent Tutoring Systems: 13th International Conference.   Zagreb, Croatia,   Jun 7-10 2016.
\item Antonucci, Alessandro and Corani, Giorgio (2017).   The multilabel naive credal classifier.   International Journal of Approximate Reasoning. 83 , 320–336.
\item Cabañas, Rafael and Antonucci, Alessandro and Cano, Andrés and Gómez-Olmedo, Manuel (2017).   Evaluating interval-valued influence diagrams.   International Journal of Approximate Reasoning. 80 , 393–411.
\item Soullard, Yann and Antonucci, Alessandro and Destercke, Sebastien (2016).   Technical gestures recognition by set-valued hidden Markov models with prior knowledge.   In Ferraro, Maria Brigida and Giordani, Paolo and Vantaggi, Barbara and Gagolewski, Marek and Gil, María Ángeles and Grzegorzewski, Przemysław and Hryniewicz, Olgierd (Eds), Soft Methods for Data Science (SMPS 2016: Proceedings of the Eight International Conference on Soft Methods in Probability and Statistics).   Rome, Italy, Sep 12-14 2016.   Advances in Intelligent Systems and Computing 456, Springer, 455–462.
\item de Campos, Cassio Polpo and Antonucci, Alessandro (2015).   Imprecision in Machine Learning and AI.   The IEEE Intelligent Informatics Bulletin. 16 (1), 20–23.
\item Antonucci, Alessandro and Scanagatta, Mauro and Mauá, Denis Deratani and de Campos, Cassio Polpo (2015).   Early classification of time series by hidden Markov models with set-valued parameters.   In Proceedings of the NIPS Time Series Workshop 2015.   Montréal, Canada,   Dec 11, 2015.
\item Mauá, Denis Deratani and Antonucci, Alessandro and de Campos, Cassio Polpo (2016).   Hidden Markov models with set-valued parameters.   Neurocomputing. 180 , 94–107.
\item Antonucci, Alessandro and Corani, Giorgio (2015).   The multilabel naive credal classifier.   In Augustin, Thomas and Doria, Serena and Miranda, Enrique and Quaeghebeur, Erik (Eds), ISIPTA ’15: Proceedings of the Ninth International Symposium on Imprecise Probability: Theories and Applications.   Pescara, Italy,   Jul 20-24 2015.   SIPTA.
\item Cabañas, Rafael and Antonucci, Alessandro and Cano, Andrés and Gómez-Olmedo, Manuel (2015).   Variable elimination for interval-valued influence diagrams.   In Destercke, Sébastien and Denoeux, Thierry (Eds), ECSQARU 2013: Proceedings of the 13th European Conference on Symbolic and Quantitative Approaches to Reasoning with Uncertainty.   Compiègne, France, Jul 15-17 2015.   Lecture Notes in Artificial Intelligence 9161, Springer, Cham, 541–551.
\item De Bock, Jasper and de Campos, Cassio Polpo and Antonucci, Alessandro (2014).   Global sensitivity analysis for MAP inference in graphical models.   In Advances in Neural Information Processing Systems 27 (NIPS 2014).   Montréal, Canada,   Dec 8-13 2014.
\item Corani, Giorgio and Antonucci, Alessandro and Mauá, Denis Deratani and Gabaglio, Sandra (2014).   Trading off speed and accuracy in multilabel classification.   In van der Gaag, Linda C. and Feelders, Ad (Eds), PGM ’14: Proceedings of the Seventh European Workshop on Probabilistic Graphical Models.   Utrecht, The Netherlands,   Sep 17-19 2014.   Springer.
\item Mauá, Denis Deratani and de Campos, Cassio Polpo and Benavoli, Alessio and Antonucci, Alessandro (2014).   Probabilistic inference in credal networks: new complexity results.   Journal of Artificial Intelligence Research. 50 , 603–637.
\item Antonucci, Alessandro and de Campos, Cassio Polpo and Huber, David and Zaffalon, Marco (2015).   Approximate credal network updating by linear programming with applications to decision making.   International Journal of Approximate Reasoning. 58 , 25–38.
\item Mauá, Denis Deratani and de Campos, Cassio Polpo and Antonucci, Alessandro (2014).   Hidden Markov models with imprecisely specified parameters.   In BRACIS 2014: Proceedings of the Brazilian Conference on Intelligent Systems.   São Carlos, São Paulo, Brazil,   Oct 18-23 2014.
\item Antonucci, Alessandro and de Rosa, Rocco and Giusti, Alessandro and Cuzzolin, Fabio (2015).   Robust classification of multivariate time series by imprecise hidden Markov models.   International Journal of Approximate Reasoning. 56 (B), 249–263.
\item Antonucci, Alessandro and Karlsson, Alexander and Sundgren, David (2014).   Decision making with hierarchical credal sets.   In Laurent, A. and Strauss, O. and Bouchon-Meunier, B. and Yager, R.R. (Eds), Information Processing and Management of Uncertainty in Knowledge-Based Systems.   Montpellier, France,   Jul 15-19 2014.   Springer.
\item Antonucci, Alessandro and de Campos, Cassio Polpo and Huber, David and Zaffalon, Marco (2013).   Approximating credal network inferences by linear programming.   In van der Gaag, Linda C. (Eds), Proceedings of the 12th European Conference on Symbolic and Quantitative Approaches to Reasoning with Uncertainty.   Utrecht, The Netherlands,   Jul 7-10 2013.   Springer.
\item Antonucci, Alessandro and de Rosa, Rocco and Giusti, Alessandro and Cuzzolin, Fabio (2013).   Temporal data classification by imprecise dynamical models.   In Cozman, Fabio Gagliardi and Denoeux, T. and Destercke, Sebastien and Seidenfeld, Teddy (Eds), ISIPTA ’13: Proceedings of the Eighth International Symposium on Imprecise Probability: Theories and Applications.   Compiègne, France,   Jul 2-5 2013.   SIPTA.
\item Antonucci, Alessandro and Huber, David and Zaffalon, Marco and Luginbühl, Philippe and Chapman, Ian and Ladouceur, Richard (2013).   CREDO: a military decision-support system based on credal networks.   In Proceedings of the 16th Conference on Information Fusion (FUSION 2013).   Istanbul, Turkey,   Jul 9-12 2013.
\item Antonucci, Alessandro and Corani, Giorgio and Mauá, Denis Deratani and Gabaglio, Sandra (2013).   An Ensemble of Bayesian Networks for Multilabel Classification.   In Proceedings of the 23rd International Joint Conference on Artificial Intelligence (IJCAI-13).   Beijing, China,   Aug 3-9 2013.
\item Mauá, Denis Deratani and de Campos, Cassio Polpo and Benavoli, Alessio and Antonucci, Alessandro (2013).   On the Complexity of Strong and Epistemic Credal Networks.   In Nicholson, Ann and Smyth, Padhraic (Eds), Proceedings of the 29th Conference on Uncertainty in Artificial Intelligence.   Bellevue, Washington,   Jul 11-15 2013.
\item Antonucci, Alessandro (2012).   An Interval-Valued Dissimilarity Measure for Belief Functions Based on Credal Semantics.   In Denoeux, T. and M.H., Masson (Eds), Belief Functions: Theory and Applications - Proceedings of the 2nd International Conference on Belief Functions.   Compiègne, France,   9-11 May 2012.   Springer.
\item Antonucci, Alessandro (2011).   The Imprecise Noisy-OR Gate.   In FUSION 2011: Proceedings of the 14th International Conference on Information Fusion.   Chicago, Illinois, USA,   Jul 5-8 2011.   IEEE.
\item Antonucci, Alessandro (2008).   Imprecise Probabilistic Graphical Models: Equivalent Representations, Inference Algorithms and Applications.   Ph.D. Thesis, Università della Svizzera Italiana.
\item Antonucci, Alessandro and Benavoli, Alessio and Zaffalon, Marco and de Cooman, Gert and Hermans, Filip (2009).   Multiple model tracking by imprecise Markov trees.   In FUSION 2009: Proceedings of the 12th International Conference on Information Fusion.   Seattle, Washington, USA,   Jul 6-9 2009.   IEEE.
\item Antonucci, Alessandro and Brühlmann, Ralph and Piatti, Alberto and Zaffalon, Marco (2007).   Credal networks for military identification problems.   In de Cooman, Gert and Vejnarová, Jirina and Zaffalon, Marco (Eds), ISIPTA ’07: Proceedings of the fifth International Symposium on on Imprecise Probability: Theories and Applications.   Prague, Czech Republic,   Jul 16-19 2007.   Action M Agency.
\item Antonucci, Alessandro and Brühlmann, Ralph and Piatti, Alberto and Zaffalon, Marco (2009).   Credal networks for military identification problems.   International Journal of Approximate Reasoning. 50 (2), 666–679.
\item Antonucci, Alessandro and de Campos, Cassio Polpo (2011).   Decision Making by Credal Nets.   In Proceedings of the International Conference on Intelligent Human-Machine Systems and Cybernetics (IHMSC 2011).   Hangzhou, China,   Aug 26-27 2011.   IEEE.
\item Antonucci, Alessandro and Cattaneo, Marco and Corani, Giorgio (2012).   Likelihood-Based Robust Classification with Bayesian Networks.   In Greco, Salvatore and Bouchon-Meunier, Bernadette and Coletti, Giulianella and Fedrizzi, Mario and Matarazzo, Benedetto and Yager, Ronald R. (Eds), Advances in Computational Intelligence.   Catania, Italy, Jul 9-13, 2012.   Communications in Computer and Information Science 299, Springer, 491–500.
\item Antonucci, Alessandro and Cattaneo, Marco and Corani, Giorgio (2011).   Likelihood-Based Naive Hierarchical Credal Classifier.   In ISIPTA ’11: Proceedings of the seventh International Symposium on Imprecise Probability: Theories and Applications.   Innsbruck, Austria,   Jul 25-28 2011.   SIPTA.
\item Antonucci, Alessandro and Corani, Giorgio and Gabaglio, Sandra (2012).   Active Learning by the Naive Credal Classifier.   In Cano, A. and Gómez-Olmedo, M. and Nielsen, T.D. (Eds), Proceeding of the sixth European Workshop on Probabilistic Graphical Models (PGM 2012).   Granada, Spain,   Sep 19-21 2012.
\item Antonucci, Alessandro and Cuzzolin, Fabio (2010).   Credal Sets Approximation by Lower Probabilities: Application to Credal Networks.   In Hüllermeier, E. and Kruse, R. and Hoffmann, F. (Eds), Computational Intelligence for Knowledge-Based Systems Design, 13th International Conference on Information Processing and Management of Uncertainty, IPMU 2010.   Dortmund, Germany,   Jun 28 - Jul 2 2010.   Springer.
\item Antonucci, Alessandro and Piatti, Alberto (2009).   Modeling unreliable observations in Bayesian networks by credal networks.   In Godo, L. and Pugliese, A. (Eds), Scalable Uncertainty Management, Third International Conference, SUM 2009.   Washington, D.C., USA,   Sep 28-30 2009.   Springer.
\item Antonucci, Alessandro and Piatti, Alberto and Zaffalon, Marco (2007).   Credal networks for operational risk measurement and management.   In Apolloni, B. and Howlett, R. J. and Jain, L. C. (Eds), Proceedings of the 11th International Conference on Knowledge-Based and Intelligent Information \& Engineering Systems: KES2007, Lectures Notes in Computer Science.   Vietri sul Mare, Italy,   Sep 12-14 2007.   Springer.
\item Antonucci, Alessandro and de Rosa, Rocco and Giusti, Alessandro (2011).   Action Recognition by Imprecise Hidden Markov Models.   In Proceedings of the 2011 International Conference on Image Processing, Computer Vision and Pattern Recognition, IPCV 2011.   Las Vegas, Nevada, USA,   Jul 18-21 2011.   CSREA Press.
\item Antonucci, Alessandro and Salvetti, Andrea and Zaffalon, Marco (2004).   Assessing debris flow hazard by credal nets.   In Lopez-Diaz, M. and Gil, M. A. and Grzegorzewski, P. and Hryniewicz, O. and Lawry, J. (Eds), Proceedings of the Second International Conference on Soft Methods in Probability and Statistics (SMPS-2004) - Soft Methodology and Random Information Systems.   Oviedo, Spain,   Sep 2-4 2004.   Springer.
\item Antonucci, Alessandro and Salvetti, Andrea and Zaffalon, Marco (2004).   Hazard assessment of debris flows by credal networks.   In Pahl-Wostl, C. and Schmidt, S. and Rizzoli, A. E. and Jakeman, A. J. (Eds), iEMSs 2004: Complexity and Integrated Resources Management, Transactions of the 2nd Biennial Meeting of the International Environmental Modelling and Software Society.   Osnanbrück, Germany,   Jun 14-17 2004.   iEMSs.
\item Antonucci, Alessandro and Salvetti, Andrea and Zaffalon, Marco (2007).   Credal networks for hazard assessment of debris flows.   In (Eds.), Progress of Artificial Intelligence in Sustainability Science, , Kropp, J., Scheffran, J., New York.
\item Antonucci, Alessandro and Yi, Sun and de Campos, Cassio Polpo and Zaffalon, Marco (2010).   Generalized loopy 2U: a new algorithm for approximate inference in credal networks.   International Journal of Approximate Reasoning. 55 (5), 474–484.
\item Antonucci, Alessandro and Zaffalon, Marco (2005).   Fast algorithms for robust classification with Bayesian nets.   In Cozman, Fabio Gagliardi and Nau, Robert and Seidenfeld, Teddy (Eds), ISIPTA ’06: Proceedings of the fourth International Symposium on Imprecise Probabilities and Their Applications.   Pittsburgh, Pennsylvania, USA,   Jul 20-23 2005.   SIPTA.
\item Antonucci, Alessandro and Zaffalon, Marco (2006).   Equivalence between Bayesian and credal nets on an updating problem.   In Lawry, J. and Miranda, E. and Bugarin, A. and Li, S. and Gil, M. A. and Grzegorzewski, P. and Hryniewicz, O. (Eds), Proceedings of third international conference on Soft Methods in Probability and Statistics (SMPS-2006).   Bristol, United Kingdom,   Sep 5-7 2006.   Springer.
\item Antonucci, Alessandro and Zaffalon, Marco (2006).   Locally specified credal networks.   In Studený, M. and Vomlel, J. (Eds), PGM’06: Proceedings of the third European Workshop on Probabilistic Graphical Models.   ,   Sep 12-15 2006.   Action M Agency.
\item Antonucci, Alessandro and Zaffalon, Marco (2008).   Decision-Theoretic Specification of Credal Networks: A Unified Language for Uncertain Modeling with Sets of Bayesian Networks.   International Journal of Approximate Reasoning. 49 (2), 345–361.
\item Antonucci, Alessandro and Zaffalon, Marco (2007).   Fast algorithms for robust classification with Bayesian nets.   International Journal of Approximate Reasoning. 44 (3), 200–223.
\item Antonucci, Alessandro and Zaffalon, Marco and Ide, Jaime S. and Cozman, Fabio Gagliardi (2006).   Binarization Algorithms for Approximate Updating in Credal Nets.   In Penserini, L. and Peppas, P. and Perini, A. (Eds), STAIRS’06: Proceedings of the third European Starting AI Researcher Symposium.   Riva del Garda, Italy,   Aug 2006.   IOS Press.
\item Antonucci, Alessandro and Zaffalon, Marco and Yi, Sun and de Campos, Cassio Polpo (2008).   Generalized loopy 2U: a new algorithm for approximate inference in credal networks.   In Jaeger, M. and Nielsen, T. D. (Eds), PGM’08: Proceedings of the Fourth European Workshop on Probabilistic Graphical Models.   Hirtshals, Denmark,   Sep 17-19 2008.
\item Benavoli, Alessio and Antonucci, Alessandro (2009).   Aggregating Imprecise Probabilistic Knowledge.   In ISIPTA ’09: Proceedings of the Sixth International Symposium on Imprecise Probability: Theories and Applications.   Durham, United Kingdom,   Jul 14-18 2009.   SIPTA.
\item Benavoli, Alessio and Antonucci, Alessandro (2010).   Aggregating Imprecise Probabilistic Knowledge: application to Zadeh’s paradox and sensor networks.   International Journal of Approximate Reasoning. 51 (9), 1014–1028.
\item de Cooman, Gert and Hermans, Filip and Antonucci, Alessandro and Zaffalon, Marco (2009).   Epistemic irrelevance in credal networks: the case of imprecise Markov trees.   In ISIPTA ’09: Proceedings of the Sixth International Symposium on Imprecise Probability: Theories and Applications.   ,   Jul 14-18 2009.   SIPTA.
\item de Cooman, Gert and Hermans, Filip and Antonucci, Alessandro and Zaffalon, Marco (2010).   Epistemic irrelevance in credal nets: the case of imprecise Markov trees.   International Journal of Approximate Reasoning. 51 (9), 1029–1052.
\item Corani, Giorgio and Antonucci, Alessandro and de Rosa, Rocco (2012).   Compression-based AODE classifiers.   In De Raedt, L. and Bessiere, C. and Dubois, D. and Doherty, P. and Frasconi, P. and Heintz, F. and Lucas, P.J.F. (Eds), Proceedings 20th European Conference on Artificial Intelligence (ECAI 2012).   Montpellier, France,   Aug 27-31 2012.   IOS Press.
\item Piatti, Alberto and Antonucci, Alessandro and Zaffalon, Marco (2010).   Building knowledge-based expert systems: a tutorial.   In Baswell, A.R. (Eds.), Advances in Mathematics Research, 11, Nova Science Publishers, New York.
\item Salvetti, Andrea and Antonucci, Alessandro and Zaffalon, Marco (2008).   Spatially distributed identification of debris flow source areas by credal networks.   In Sànchez-Marrè, M. and Béjar, J. and Comas, J. and Rizzoli, A. E. and Guariso, G. (Eds), iEMSs 2008: International Congress on Environmental Modelling and Software Integrating Sciences and Information Technology for Environmental Assessment and Decision Making (Transactions of the 4th Biennial Meeting of the International Environmental Modelling and Software Society).   Barcelona, Catalonia,   Jul 2008.   iEMSs.
\end{cvitems}
\end{cventries}
\vskip 2mm
