%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Students Supervision}
%-------------------------------------------------------------------------------
\begin{cvskills}
%---------------------------------------------------------
\cvskill{Lilith Mattei}{Ph.D. Student Supervision, USI, 2020 (ongoing).}
\cvskill{Nicol Allegra}{Master Thesis Supervision, SUPSI, 2021.}
\cvskill{}{\emph{Explainability in Reinforcement Learning by Saliency Maps with Applications to Warfare Simulation.}}
\cvskill{Simone Mellace}{Master Thesis Supervision, SUPSI, 2020.}
\cvskill{}{\emph{NOVEL2GRAPH: Knowledge Graphs and Dynamic Embeddings for Narrative Text Understanding.}}
\cvskill{Denis Broggini}{Master Thesis Co-Supervision, SUPSI, 2020.}
\cvskill{}{\emph{Bayesian Conversational Recommendation System.}}
\cvskill{Thomas Tiotto}{Master Thesis Supervision, USI, 2019.}
\cvskill{}{\emph{Explainable AI with Probabilistic Graphical Models. A Study with Application and Evaluation on a Medical Domain.}}
\cvskill{Edvin Jonuzoski}{Master Thesis Co-Supervision, USI, 2014.}
\cvskill{}{\emph{Adaptive Testing by Bayesian Networks.}}
\cvskill{Rocco de Rosa}{Master Thesis Co-Supervision, Faculty of Informatics, Universit\`a degli Studi di Milano, 2011.}
\cvskill{}{\emph{Time series classification by precise and imprecise Markov models with applications in action recognition.}}
\cvskill{Sandra Gabaglio}{Master Thesis Co-Supervision, SUPSI, 2012.}
\cvskill{}{\emph{E-coaching system, approximate reasoning and similarity analysis by Bayesian networks.}}
\cvskill{Mikol Faro}{Master Thesis Co-Supervision, SUPSI, 2012.}
\cvskill{}{\emph{Credal networks decision support system JavaQCredo.}}
\\
\cvskill{External Examiner}{Renato Geh (M.Sc., University of S\~ao Paulo, 2022), Martin Plajner (Ph.D., University of Prague, 2021),}
\cvskill{}{Angela McCourt (Ph.D., Trinity College Dublin, 2019),  Rafael Caba\~nas (Ph.D., University of Granada, 2017),}
\cvskill{}{Gen Yang (Ph.D., University of Compiegne, 2016).}
\end{cvskills}
