%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Talks}
\begin{cventries}

%\section{Tutorials}
\cventry{2015}{A. Antonucci, G. Corani and C.P. De Campos}
{Sensitivity Analysis in Graphical Models with Imprecise Probabilities: Applications to Robust Data Mining and Decision Support Systems}
{IJCAI '15}{(24th Int. Joint Conf. on Artificial Intelligence)}{}
\cventry{2013}{A. Antonucci, G. Corani and D. Mau\'a}
{Bayesian networks with imprecise probabilities: theory and applications to knowledge-based systems and classification}
{IJCAI '13}{(23rd Int. Joint Conf. on Artificial Intelligence)}{}
\cventry{2010}{A. Antonucci, G. Corani and C. P. De Campos}
{Classification with Imprecise Probabilities}
{4th SIPTA Summer School, Durham}{}{}
\cventry{2010}{A. Antonucci, G. Corani}
{Bayesian Networks with Imprecise Probabilities: Theory and Applications to Knowledge-based Systems and Classification}
{ AAAI-10: Twenty-Fourth Conference on Artificial Intelligence}{}{}

I also gave lectures on credal networks and imprecise probability during the SIPTA Summer School on Imprecise Probability (\url{www.sipta.org}), editions 2010, 2012, 2014, and during the Imprecise Probabilities Workshop (May 2015).



  \cventry
    {Presenter for <Hosting Web Application for Free utilizing GitHub, Netlify and CloudFlare>} % Role
    {DevFest Seoul by Google Developer Group Korea} % Event
    {Seoul, S.Korea} % Location
    {Nov. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Introduced the history of web technology and the JAM stack which is for the modern web application development.}
        \item {Introduced how to freely host the web application with high performance utilizing global CDN services.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Presenter for <Metasploit 101>} % Role
    {6th Hacking Camp - S.Korea} % Event
    {S.Korea} % Location
    {Sep. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Introduced basic procedure for penetration testing and how to use Metasploit}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
